Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-06-22 doc/main_jfm.tex
updates

The preliminary test of the proposed model using integral equation method is the Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate. A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$. Based on the theoretical Jeffery orbits with respect to the target angle $\chi(t)$,

@@

For the target bilayer, a circular initial shape is chosen to perform the relaxation run. This vesicle consists 
of $N=58$ disks with radius $r=0.5$ and the starting diameter for the vesicle is $\sim8.5$.
The starting center of mass position of the vesicle is pinned at the origin and we track particle velocities 
to determine the initial configuration for later simulations. This will prevent some numerical instability issues when the minimum of the total energy is not achieved. For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
Figure~\ref{figure2} shows that the magnitudes of velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim1/3.74N$. The time step size 
$\Delta t=0.2$ is used for all simulations including the relaxation run.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{relax.eps}
  \caption{Vesicle relaxes under a quiescent flow. The blue dashed curve and the red solid curve are mean magnitudes of the particle velocities. The black dashed line shows the reference of how velocity magnitudes 
  decay.
  }
    \label{figure2}
\end{figure}

The snapshots of the simulation for single vesicle in a shear flow is shown in Figure~\ref{figure3}.
Panel (a) shows the initial circular shape obtained from the relaxation run and the deformed 
configuration of the vesicle after a period of time is in panel (c). The color presented in the figure 
is the strength of the action due to the hydrophobic attraction. From weak to strong action field, the color
varies from blue to red.
To demonstrate the tank-treading behavior of the vesicle, panels (b) and (d) provide the fluid velocities 
over the whole computational domain when the shear flow passes through the vesicle.

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.0025$: 
  (a) Initial configuration of 58-body vesicle; 
  (b) The fluid velocity plot with respect to the configuration in (a);
  (c) Deformed vesicle after $20000$ steps. The tank-treading motion occurs after reaching the state shown in panel (c).
  (d) The fluid velocity plot with respect to the configuration in (c);
  The background colors in panels (a) and (c) represent the strength of the hydrophobic attraction potential. The blue region shows no action and the red region with the bilayer gives the strongest 
  action.
  }
    \label{figure3}
\end{figure}
%

@@

\begin{figure}
\centering
\includegraphics[width=0.24\textwidth]{N116_ext_vel_0.pdf}
\includegraphics[width=0.24\textwidth]{N116_ext_vel_2500.pdf}
\includegraphics[width=0.24\textwidth]{N116_ext_vel_5000.pdf}
\includegraphics[width=0.24\textwidth]{N116_ext_vel_7500.pdf}
  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
    \label{figure6}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_ext_0.pdf}
\includegraphics[height=1.2in]{N116_shear_3000.pdf}
\includegraphics[height=1.2in]{N116_shear_6000.pdf}
\includegraphics[height=1.2in]{N116_shear_9000.pdf}\\
  \caption{Two vesicles under a shear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels.
  }
    \label{figure7}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.24\textwidth]{N116_shear_vel_0.pdf}
\includegraphics[width=0.24\textwidth]{N116_shear_vel_3000.pdf}
\includegraphics[width=0.24\textwidth]{N116_shear_vel_6000.pdf}
\includegraphics[width=0.24\textwidth]{N116_shear_vel_9000.pdf}
  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
    \label{figure8}
\end{figure}

>>>>

The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate. An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$. Based on the theoretical Jeffery orbits with respect to the target angle $\chi(t)$,

@@

For the target bilayer, a circular initial shape is chosen to perform the relaxation run. This vesicle-like 
structure consists of $N=58$ disks with radius $r=0.5$ and the starting diameter for the vesicle is about 
$8.5$ length units.
The starting center of mass position of the vesicle is pinned at the origin and we track particle velocities 
to determine the initial configuration for later use such as single and multiple vesicle simulations. This will prevent some numerical instability issues when the minimum of the total energy is not achieved. For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
Figure~\ref{figure2} shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005t$. In the same figure, the variation of mean particle orientation $\theta$ also decreases as expected. The time step size 
$\Delta t=0.2$ is used for all simulations including the relaxation run.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{relax.eps}
  \caption{Vesicle relaxes under a quiescent flow. The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively. The red curve shows the decreasing trend of the mean magnitude of particle orientation change. The black dashed line shows the reference of how all magnitudes decay.
  }
    \label{figure2}
\end{figure}

The snapshots of the simulation for single vesicle in a shear flow are shown in Figure~\ref{figure3}.
Panel (a) shows the initial circular shape obtained from the relaxation run and the deformed 
configuration of the vesicle after a period of time ($t=4000$) is in panel (c). The color presented in the figure 
is the strength of the action due to the hydrophobic attraction. From weak to strong action field, the color
varies from blue to red.
To demonstrate the tank-treading behavior of the vesicle, panels (b) and (d) provide the streamlines of the 
fluid velocity over the whole computational domain when the shear flow passes through the vesicle. The tank-treading motion of the structure is observed.

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.0025$: 
  (a) Initial configuration of 58-body vesicle; 
  (b) The fluid velocity plot with respect to the configuration in (a); Streamlines are plotted in the background
  as solid curves. Red arrows represent the particle velocities.
  (c) Deformed vesicle after $20000$ steps. The tank-treading motion occurs after reaching the state shown in panel (c).
  (d) The fluid velocity plot with respect to the configuration in (c);
  The background colors in panels (a) and (c) represent the strength of the hydrophobic attraction potential. The blue region shows no action and the red region with the bilayer gives the strongest action.
  }
    \label{figure3}
\end{figure}
%

@@

%\begin{figure}
%\centering
%\includegraphics[width=0.24\textwidth]{N116_ext_vel_0.pdf}
%\includegraphics[width=0.24\textwidth]{N116_ext_vel_2500.pdf}
%\includegraphics[width=0.24\textwidth]{N116_ext_vel_5000.pdf}
%\includegraphics[width=0.24\textwidth]{N116_ext_vel_7500.pdf}
%  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
%    \label{figure6}
%\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_shear_0.pdf}
\includegraphics[height=1.2in]{N116_shear_3000.pdf}
\includegraphics[height=1.2in]{N116_shear_6000.pdf}
\includegraphics[height=1.2in]{N116_shear_9000.pdf}\\
  \caption{Two vesicles under a shear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels.
  }
    \label{figure7}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=0.24\textwidth]{N116_shear_vel_0.pdf}
%\includegraphics[width=0.24\textwidth]{N116_shear_vel_3000.pdf}
%\includegraphics[width=0.24\textwidth]{N116_shear_vel_6000.pdf}
%\includegraphics[width=0.24\textwidth]{N116_shear_vel_9000.pdf}
%  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
%    \label{figure8}
%\end{figure}
